---
title: "Latent Factor Influence Model"
author: "Shimeng Dai"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r, echo=FALSE}
setwd("~/Desktop/Michigan State/Second semeter/Network Analysis")
```

### Set your working directory 

```{r}
# uncomment and insert your working directory
#setwd("")
```
 
### Load necessary packages 

```{r, message=FALSE, warning=FALSE}

#install packages first if you haven't
#install.packages("")
library(RSiena)
library(sna)
library(statnet)
library(latentnet)
library(igraph)
``` 


### Load data

```{r}
#Read data - assuming data are in current working directory
Toyatt <-read.csv("Toyatt.csv")
Toynet <-read.csv("Toynet.csv")

```

### Change the datasets to the right formats

```{r}

Toynet.data <- graph.data.frame(Toynet)
Toynet.adj <-get.adjacency(Toynet.data, sparse = FALSE, attr='weight')
g1 <- network(as.matrix(Toynet.adj))
Toynet.m <- as.matrix(Toynet.adj)

```

### Attach attributes to network

```{r}
g1%v%"attr1" <- Toyatt[,2]
g1%v%"attr2" <- Toyatt[,3]
g1%v%"cattr3" <- Toyatt[,4]
```

### Find latent positions

```{r,warning=FALSE}
# set.seed otherwise the plot change every time you run the code
set.seed(57)
m1<-ergmm(g1 ~ euclidean(d = 2)+absdiff("attr1")+absdiff("attr2")+absdiff("cattr3"),control=ergmm.control(sample.size=5000,burnin=20000,interval=10,Z.delta=5))
plot(m1)
```

```{r}
#Two latent positions
m1$mkl$Z
```

#### Save the first latent position

```{r}
latent_pos1<-rep(m1$mkl$Z[,1],2)
latent_pos1
```



#### Save the second latent position

```{r}
latent_pos2<-rep(m1$mkl$Z[,2],2)
latent_pos2

```

#### Calculate the exposure term

```{r}
E<-matrix(0,6,3)
for (i in 1:6)
{    #making exposure term
  if (sum(Toynet.m[i,])!=0)
    E[i,1]<-(Toynet.m[i,]%*%Toyatt[,2])/sum(Toynet.m[i,])
  if (sum(Toynet.m[i,])!=0)
    E[i,2]<-(Toynet.m[i,]%*%Toyatt[,3])/sum(Toynet.m[i,])
}
```

#### Format variables

```{r}
att_1_2<-c(Toyatt[,2],Toyatt[,3])
expo<-c(E[,2],E[,1])
cattr3 <-rep(Toyatt[,4],2)
```

#### Combine variables

```{r}
infl<-data.frame(cbind(latent_pos1, latent_pos2, att_1_2, cattr3, expo, rep(c(1:6),2),rep(c(1:2),each=6)))
```

### Model 1   (predictor: exposure term) 

```{r}
summary(lm(att_1_2~expo ,data=infl))

```

### Model 2   (predictors: exposure term and latent position 1)

```{r}
summary(lm(att_1_2~expo+latent_pos1,data=infl))
```

### Model 3   (predictors: exposure term, latent position 1 and 2)

```{r}
summary(lm(att_1_2~expo + latent_pos1 + latent_pos2,data=infl))
```

### Model 4   (predictors: exposure term, latent position 1, 2, and categorical variable)

```{r}
summary(lm(att_1_2~expo + latent_pos1 + latent_pos2 + cattr3 ,data=infl))

```