---
title: "Edgelist_nodelist"
author: "Nicole Jess, Yuqing Liu"
date: "`r format(Sys.time(), '%Y-%m-%d, %H:%M:%S %Z')`"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    code_folding:  show
params: 
  outfile: "create-social-network-data.html"
---

# Purpose
This script restructures data scraped from Twitter into a format that can be used 
for social network analysis.



# Load R Packages
Load contributed R packages that we need to get additional functions. 

``` {r, warning = FALSE}
library(tidyverse)          # dplyr, ggplot2, tidyr, etc.
library(here)               # for here()
library(linkcomm)           # for integer.edgelist()
library(igraph)             # for graph_from_data_frame()

```

# Load data and insert your bearer_token

```{}

bearer_token <- ""


```

```{r}
setwd("/Users/shimengdai/Dropbox/Michigan State/Eighth semester/SNA_Materials/2024 SNA workshop/data")

load("all_tweets.RData")
```

# Edgelist
Interaction information is extracted from the Tweet data and restructured into 
an edgelist.

```{r edges}


edgelist <- all_tweets %>% # If you have a dataset with a different name, be sure to replace all_tweets to your dataset name
  unnest(entities) %>%
  unnest_longer(mentions) %>%
  mutate(to=mentions$id) %>%
  rename(tweet_id=id,
         from=author_id) %>%
  drop_na(to,from) %>%
  select(tweet_id, created_at, from, to, text)

```

Altogether, this gives us a total of `r nrow(edgelist)` edges in this network. 

# Integer edgelist

Some social network tools we work with require that the edge IDs are integers 
starting with 1. This code creates an edgelist that meets these requirements.

```{r integer-edges}

# integer edgelist
network1 <- edgelist %>%
  select(from,to) %>%
  as.matrix() %>%
  integer.edgelist()

int_edges <- network1$edges %>%
  as.data.frame() %>%
  rename(from = V1,
         to = V2) %>%
  group_by(from,to) %>%
  summarize(weight = n()) %>%
  as.data.frame()

# save indegree and outdegree to use as node attributes
indegree <- int_edges %>%
  group_by(to) %>%
  summarize(indegree=n()) %>%
  as.data.frame()

outdegree <- int_edges %>%
  group_by(from) %>%
  summarize(outdegree=n()) %>%
  as.data.frame()

```


# Nodelist

This code creates a list of all the nodes in the network and pulls information from 
those Twitter user profiles. 

```{r}
ids <- c(edgelist$from, edgelist$to) %>% unique()
length(ids)
ids <- paste(ids, collapse = ',') # doesn't work when n>100 (user rate limit is 100)
                                   # but I think we should be able to go up to 500 (rate limit for apps)

# Split the string into individual IDs
user_id_vector <- unlist(strsplit(ids, ","))

# Function to split the vector into chunks of 100
split_into_chunks <- function(vec, chunk_size) {
  split(vec, ceiling(seq_along(vec) / chunk_size))
}

# Split into chunks of 100
chunks <- split_into_chunks(user_id_vector, 100)

# Reassemble each chunk as a comma-separated string
chunked_strings <- sapply(chunks, paste, collapse = ",")

# Print the chunked strings
print(chunked_strings)

id_group1 <- chunked_strings[[1]]
id_group1
```

## Test scraping with the first 100 ids (id_group1)

```{r}
id_string <- id_group1 

params_users <- list(`ids` = id_string,
                     `user.fields` = 'created_at,description,entities,id,location,name,public_metrics,username,verified')


# Create the endpoint URL with the comma-separated user IDs
url <- paste0("https://api.twitter.com/2/users?ids=", id_string)

# Send the GET request to Twitter API with the correct Authorization header
response <- httr::GET(url,
                      httr::add_headers(Authorization = paste('Bearer', bearer_token)),query = params_users)

# Extract the response content, simplifying it into a dataframe for easy use
users_data <- httr::content(response, as = 'parsed', type = 'application/json', simplifyDataFrame = TRUE)

```

## Create nodelist

```{r}
  # Create a dataframe from the main fields
  nodelist <- as.data.frame(users_data$data) %>%
    # Unnest the public_metrics column (which is a list)
    unnest_wider(public_metrics, names_sep = "_") %>%
    # Unnest other relevant nested columns as needed
    unnest_wider(entities, names_sep = "_", names_repair = "minimal") %>%
    select(id, name, username, created_at, description, location, verified, 
           public_metrics_followers_count, public_metrics_following_count, 
           public_metrics_tweet_count, public_metrics_listed_count)

```


# Save Data

```{r save-t2-data}

# save as R objects

save(edgelist, file=here("edgelist_test.RData"))
save(nodelist, file=here("nodelist_test.RData"))

# save as csv files

write.csv(edgelist, "edgelist.csv")
write.csv(nodelist, "nodelist.csv")


```
