---
title: "The Influence Model with Twitter Data"
output: html_document
date: "2024-05-08"
author: Shimeng Dai 
---


## Load required libraries

```{r,warning=FALSE}
library(tidyverse)
library(dplyr)
library(stringr)
library(ggplot2)
library(lubridate)
library(RColorBrewer)
```

## Load required datasets (tweets and keywords)


```{r}

# The data was scraped using the following keywords:

# query = "((graduate OR grad) 
                    # (student OR assistant OR worker) 
                    # (union OR unionization OR wages OR healthcare OR NLRB OR labor OR contract OR strike) 
                    # (-isreal)) # if you want to remove tweets contain Isreal
         # (is:retweet OR is:reply OR is:quote OR has:mentions)
         # lang:en"

# Time frame of the data: from late January to late April

setwd("/Users/shimengdai/Dropbox/Michigan State/Eighth semester/SNA_Materials/2024 SNA workshop/data")

# Twitter network data
load("edgelist.RData")
df <- edgelist

# Dictionary data 
# Use to identify if a tweet contains specific words
# You need to identify your own dictionary data for your specific topic
word <- read.csv("Dictionary.csv") 
word <- as.data.frame(word)
head(word, n = 5)
```


## Remove irrelevant tweets

```{r}

# Preprocess the text: convert to lowercase and remove punctuation
df$text_cleaned <- tolower(df$text)
df$text_cleaned <- str_replace_all(df$text_cleaned, "[[:punct:]]", "") # removes punctuation

# Define and preprocess the strings to remove
# Incude tweets that you would like to remove from the dataset

raw_strings_to_remove <- c(
  "I'm proud to bring Dr. Intimaa Salama, a Palestinian graduate student at @SLU_Official and dentist, as my guest to the State",
  "Since Oct. 7, the IDF has killed more than 30,000 Palestinians. This includes 35 of Dr. Intimaa Salama’s family members",
  "Rep. Cori Bush, who has been outspoken in her criticism of Israel’s actions in Gaza, has invited a Palestinian graduate",
  "Israeli forces just invaded Ramallah it is almost 4:00 AM local.
They arrested a graduate student Layan Kayed and sho",
"I was very disappointed that the Harvard Law Student Government endorsed divesting in Israel",
"As they purport to champion freedom of expression on campus, Harvard anti-Israel protesters (including the BDS caucus of",
"As they purport to champion freedom of expression on campus, Harvard anti-Israel protesters",
"that's my school! my grad student labor is directly funding investments in israeli currency",
"This is absolutely nothing compared with what is being inflicted upon the people of Gaza",
"Breaking: The “Resolution affirming the need for a permanent ceasefire in Gaza and ceasing MIT labor support for Isr",
"UAW graduate students at the University of Southern California joined the walkout for Palestine during their picket line",
"Cori Bush's guest to the State of the Union tonight is a Palestinian dental student from her district who has lost dozens",
"a Palestinian grad student who lost 35 family members in Gaza"
)

strings_to_remove <- sapply(raw_strings_to_remove, function(x) {
  x <- tolower(x)
  str_replace_all(x, "[[:punct:]]", "") # more consistent punctuation removal
})

# Debug print to verify strings are processed as expected
print(head(strings_to_remove, 2))

# Filter the data by checking for non-presence of each string to remove
for (string in strings_to_remove) {
  df <- df[!grepl(pattern = string, df$text_cleaned, fixed = TRUE), ]
}

# Check the resulting filtered data
head(df, 5)

```


```{r}
nrow(edgelist) # Original sample size
nrow(df) # After removing irrelevant tweets
nrow(edgelist) - nrow(df) # The number of tweets removed
```



## Plot the tweet frequency over time 
## Divide the time period into three time intervals

```{r}

# Convert created_at to Date object
tweets <- df
tweets$created_at <- as.Date(tweets$created_at)

# Aggregate tweets by date
daily_tweets <- aggregate(tweet_id ~ created_at, data = tweets, FUN = length)

# Rename the columns for clarity
colnames(daily_tweets) <- c("Date", "Number_of_Tweets")


# Find the maximum number of tweets for setting limits
max_tweets <- max(daily_tweets$Number_of_Tweets)


daily_tweets$Date <- ymd(daily_tweets$Date)

# Define peak periods
peak_start <- ymd("2024-04-02")
peak_end <- ymd("2024-04-10")

# Create the plot
ggplot(daily_tweets, aes(x = Date, y = Number_of_Tweets)) +
  geom_line() +
  scale_x_date(date_breaks = "3 days", date_labels = "%b %d") +
  scale_y_continuous(breaks = seq(0, max(daily_tweets$Number_of_Tweets, na.rm = TRUE), by = 500)) + # Adjust 'by' as needed
  geom_vline(xintercept = as.numeric(peak_start), linetype = "dashed", color = "red") +
  geom_vline(xintercept = as.numeric(peak_end), linetype = "dashed", color = "blue") +
  theme_minimal() +
  labs(title = "Number of Tweets Over Time", x = "Date", y = "Number of Tweets") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Adjust text angle for better visibility

```


## Tweet preprocessing 
## Keyword searching method

```{r}


# Exclude URL patterns in Text
tweets$text <- gsub("http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\\(\\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+", "" ,tweets$text)

# Exclude @user patterns in Text
tweets$text <- gsub("@\\w+", "" ,tweets$text)
#tweets$text <- gsub("\\w+", "" ,tweets$text)


# Exclude hashtags patterns in Text
tweets$text <- gsub("#", "" ,tweets$text)



find_keywords <- function(text, keywords){
  text <- tolower(text)
  count <- 0
    for (ch in keywords) {
      if (grepl(ch, text)){
  
        if (ch != ""){
          count <- count + 1
        }
      }
   }
  return(count)
}
#qqq
word <- tolower(word$keyword)

# The number of keywords found in each tweet

tweets$num <- lapply(tweets$text, FUN = find_keywords, keywords = word)

# A binary variable represents whether a tweet contains at least one keyword
tweets$num_b  <- ifelse(tweets$num  > 0, 1, 0)

tweets$num <- as.numeric(tweets$num)

head(tweets, n = 5)

```


## Save tweets as R data

```{r}
save(tweets,file = "tweets.RData")
```

## Plot the distribution of relevant and irrelevant tweets


```{r}
# Assuming tweets$num_b contains the relevant and irrelevant tweet codes
code_counts <- table(tweets$num_b)

# Plot the bar chart
bar_positions <- barplot(code_counts,
  main = "The Histogram of Word Use",
  xlab = "Code",
  ylab = "Frequency",
  col = brewer.pal(n = 3, name = "Set3")[1:2], # Specify a palette with at least 3 colors and select the first 2
  names.arg = c("Irrelevant", "Relevant"), # Labeling the bars
  ylim = c(0, max(code_counts) + 1000)
)

# Add the count number on each bar
text(x = bar_positions, y = code_counts, label = code_counts, pos = 3, cex = 1, col = "black")
```

## Plot the word use in relevant tweets

```{r}

hist(
  tweets$num, 
  main="The Histgram of The Word Frequency",
  xlab="The Number of Words",
  col="#006600"
  )

```

## Divide data into three time intervals

```{r}

# Divide the data into three intervals based on the peak dates
t1 <- tweets %>% filter(created_at < peak_start)
t2 <- tweets %>% filter(created_at >= peak_start & created_at <= peak_end)
t3 <- tweets %>% filter(created_at > peak_end)
```

## Find unique users across three time intervals


```{r}
# During T2, a sender is defined as someone who sends, replies, quotes, or retweets a tweet. A sender can be viewed as a nominee, who nominates others that they have interacted with before or have been affected by their activities on Twitter.

# Find senders during T1 
unique_from_interval1 <- unique(t1$from)

# Final senders and receivers during T2
unique_from_interval2 <- unique(t2$from)
unique_to_interval2 <- unique(t2$to)
unique_people_interval2 <- union(unique_from_interval2, unique_to_interval2)

# Find senders during T3
unique_from_interval3 <- unique(t3$from)

# Find the intersection of the unique lists from each interval
common_people <- Reduce(intersect, list(unique_from_interval1, unique_people_interval2, unique_from_interval3))

# Output the common people
print(common_people)
print(length(common_people))

```

## Filter the data based on the unique common users

```{r}
t1 <- t1 %>% filter(from %in% common_people)
t2 <- t2 %>% filter(from %in% common_people) %>% filter(to %in% common_people)
t3 <- t3 %>% filter(from %in% common_people)
```

## Save edgelist from t1 for KliqueFinder

```{r}

t1_num_b <- t1 %>%
  dplyr::select(from, to, num_b) %>%
  group_by(from, to) %>%
  summarise(weight = sum(num_b)) %>%
  filter(from != to)

save(t1_num_b, file = "t1edge.RData")
```

## Get T2 edgelist

```{r, warning=FALSE}

t2_num_b <- t2 %>%
  filter(num_b > 0) %>%
  dplyr::select(from, to, num_b) %>%
  group_by(from, to) %>%
  summarise(weight = sum(num_b)) %>%
  filter(from != to)

print(head(t2_num_b, n = 5))
table(t2_num_b$weight)

```

```{r}
save(t2_num_b, file = "t2edge.RData")
```

```{r, warning=FALSE}

# Generate all possible pairs of user IDs
combinations <- expand.grid(from = common_people, to = common_people, stringsAsFactors = FALSE)
colnames(combinations) <- c("from", "to")

# Filter out self-loops (where from and to are the same)
combinations <- subset(combinations, from != to)

t2_numB_list <- merge(combinations, t2_num_b, by = c("from", "to"), all.x = TRUE)
t2_numB_list$weight[is.na(t2_numB_list$weight)] <- 0

print(head(t2_numB_list, n = 5))
table(t2_numB_list$weight)

```

```{r}
save(t2_numB_list, file = "t2edge_full.RData")
```


## Save tweets

```{r}
save(tweets,file = "tweets.RData")
write.csv(tweets, "tweets.csv")
```

## Get T1 and T3 word use


```{r}

# Nominee attribute (word use) T1 
# Nominee is "to" in T2 edgelist
T1 <- t1 %>%  
  dplyr::select(from,tweet_id, created_at,text, num) %>% 
  group_by(from) %>% 
  summarise(total1 = sum(num)) 

t1.tweets <- T1 %>%
  rename(to = from)  

# Nominator attribute (word use) T3
# Nominator is "from" in T2 edgelist
T3 <- t3 %>%  
  dplyr::select(from,tweet_id, created_at,text, num)%>% 
  group_by(from) %>% 
  summarise(total3 = sum(num))

t3.tweets <- T3

```

## Calculate exposure term

```{r}
data <- t2_numB_list %>% 
  dplyr::left_join(t1.tweets, by = 'to') # attach nominee attribute to T2 edgelist 

sum(is.na(data)) # The merged dataset should not contain NAs. 
```


```{r}

# attach nominator attribute to T2 edgelist
data <- t2_numB_list %>% 
  dplyr::left_join(t1.tweets, by = 'to')  

# Calculate exposure term for each interaction
data$exposure <- data$weight * data$total1

# Calculate the mean exposure term for each user 
exposure <-
    data %>% 
    group_by(from) %>%
    summarize(mean_exposure = mean(exposure))

```



## Combine datasets

```{r}


t1.tweets <- t1.tweets %>% # rename receiver as sender to merge these
    rename("from" = "to")

final_data <- dplyr::left_join(t1.tweets, exposure, by = "from")

final_data <- dplyr::left_join(final_data, t3.tweets, by = "from") 

sum(is.na(final_data)) # Check NAs in final_data. The final_data should not contain NAs.

```

## Visualize issue use during T1 and T3

```{r}

# Word use during T1
hist(final_data$total1,
       main="Word Use (T1)",
       xlab="The Number of Words",
       col="#006600"
     )
# Word use during T3
hist(final_data$total3,
       main="Word Use (T3)",
       xlab="The Number of Words",
       col="#006600"
     )

```

## Visualize exposure term 

```{r}

# mean exposure term 
hist(
       final_data$mean_exposure,
       main="Mean Exposure (T2)",
       xlab="Mean Exposure",
       col="#006600"
     )


```


```{r}
# log mean exposure term 
hist(
     log(final_data$mean_exposure),
     main="Log Mean Exposure (T2)",
     xlab="Log Mean Exposure",
     col="#006600"
     )
```


## The influence model

```{r}
mod <- lm(total3 ~ total1 + mean_exposure, data = final_data)

summary(mod)
```

## Partial plot

```{r}
car::avPlots(mod)
```

## Partial correlation

```{r}

mod2 <- lm(total3 ~ total1, data = final_data)
mod3 <- lm(mean_exposure ~ total1, data = final_data)

final_data$R1 <- mod2$residuals
final_data$R2 <- mod3$residuals

cor(final_data$R1, final_data$R2)
```

## Save final_data

```{}
save(final_data,file = "final_data.RData")
write.csv(final_data, "final_data.csv")
```



